Stack Safety as a Security Property

### 2020-06-10 main.tex
Forgot to commit yesterday

But what {\em is} stack safety? A formal definition of stack safety is
lacking from the literature, with the notion only being defined
negatively: through examples of stack unsafety. Two classical examples
of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}

A common undertone in such examples is the intention to protect
callers from callees: a callee should be not be able to access or
overwrite a caller's private data. In this paper we turn this
intuition into a formal security property, with an integrity and
a confidentiality component.

Informally, {\em stack integrity} guarantees that if a function call
returns, the caller's stack data will be identical to what it was
before the call. {\em Stack confidentiality} ensures that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g. a caller's private data or uninitialized memory).

@@

We begin by giving some background in Section~\ref{sec:prelim}.
Our contributions are:
\begin{itemize}
\item A formal property capturing the informal understanding of what ``stack safety'' is.
\item Evidence that this property is strong enough to capture the folk
intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\end{itemize}
Finally, in Section~\ref{sec:relwork} we discuss related work and
sketch directions for future work in Section~\ref{sec:future}.

@@

@@

\sna{Trying to get at why ROP is potentially a problem in non-returning calls
     with an example.}
  \paragraph{Non-stack Resources}

>>>>

But what {\em is} stack safety? A formal definition of stack safety is
lacking from the literature, with the notion only being defined
negatively: through examples of stack unsafety. Two classical examples
of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}
\leo{Do we also need an example of ROP/control flow for the new part?}

A common undertone in such examples is the intention to protect
callers from callees: a callee should be not be able to access or
overwrite a caller's private data. In this paper we turn this
intuition into a formal security property, with a confidentiality and
an integrity component.
%
Informally, {\em stack confidentiality} ensures that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g. a caller's private data or uninitialized memory).  {\em Stack
  integrity} guarantees that if a function call returns, the caller's
stack data will be identical to what it was before the call.

@@

\leo{This will probably need to be fixed depending on what we end up
  doing}
%
A second common concern is to protect the call structure itself: a
callee should not be allowed to jump to the middle of an arbitrary
block of code either directly (via a jump instruction) or indirectly
(by corrupting stack data and returning). In this work we enforce
well-bracketed control flow by ensuring that code transitions are
valid based on a statically-known call graph of the
program. \leo{e.g. provided by the compiler?}

We begin by giving some background in Section~\ref{sec:prelim}.
Our contributions are:
\begin{itemize}
\item A formal property capturing the local state encaptulation
  notion of stack safety.
\item Evidence that this property is strong enough to capture the folk
intuition: we show that the stack
  unsafe examples from the literature also fail our property.
\item Evidence that the property is not too strong. It's realizible by
  a previously proposed  micropolicy enforcement mechanism \leo{And it
    says yes on a substantial body of code}
\item A (inductive? step-by-step/stepwise) variant of this property
  tuned for testing/verification together with a proof that it implies
  the original property.  We test the whole thing with a cool
  framework.
\item A lazy version of the property that allows for more efficient/dynamic enforcement.
  Maybe testing.
\item An extension to this formal property that enforces well-bracketed
  control flow and an accompanying policy.
\end{itemize}
Finally, in Section~\ref{sec:relwork} we discuss related work and
sketch directions for future work in Section~\ref{sec:future}.

@@

\paragraph{Examples}

@@

\sna{Trying to get at why ROP is potentially a problem in non-returning calls
     with an example.}

\paragraph{What about tail recursion and other non-stack-like control flow}

\paragraph{What about well-bracketed control flow?}

Andrew thinks it's mostly orthogonal...?

\paragraph{Adding Heap Safety}

Discuss how we would do it, referring to Arthur's paper.  Probably not very long or formal?

\paragraph{Non-stack Resources}
